---
title: "Homework 3"
author: "Riya Bhilegaonkar"
date: "2022-10-11"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Libraries and Set Chunk Options:
```{r}
library(tidyverse)
library(p8105.datasets)
library(patchwork)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1
```{r}
data("instacart")
View("instacart")


```

The dataset contains 1,384,617 observations of 131,209 unique users, where each row in the dataset is a product from an order.

## Problem 2
Loading and tidying the data
```{r}
accel_data = read_csv("data/accel_data.csv")%>% janitor::clean_names() %>%
mutate(day_type = ifelse(day == "Saturday" | day == "Sunday", "weekend", "weekday")) %>% 
drop_na() %>%
pivot_longer(activity_1:activity_1440, names_to = "activity", values_to="min_time")

View(accel_data)
```

The `accel_data` dataset has data from an accelerometer of a 63 year old male with a BMI of 25 who was diagnosed with congestive heart failure.
The resulting dataset has the 5 variables of week, day_id, day, day_type (weekday vs weekend), activity, min_time (activity count for each minute of a 24-hour day starting at midnight). There are 50400 observations and 5 variables. The dataset provides specific information on the accelerometer activity count for each minute for a particular, week, day and specific day_id, indicating distinctive days. 

Aggregate across minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?
```{r}
accel_data %>% 
pivot_wider(names_from="activity",values_from ="min_time") %>%
group_by(week, day_id, day) %>% summarise(tot_activity = rowSums(across(activity_1:activity_1440,na.rm=TRUE))) %>%
knitr::kable(digits = 2)
```

From the table there does not appear to be any obvious trends. 

Making a single-panel plot that shows the 24-hour activity time course for each day
```{r}
accel_data %>%
pivot_wider(names_from="activity",values_from ="min_time") %>%
group_by(week, day_id, day) %>% summarise(tot_activity = rowSums(across(activity_1:activity_1440,na.rm=TRUE))) %>%
ggplot(aes(x=day, y=tot_activity,group=week, color=week)) +
geom_line() +
ylab("Total Activity")+
xlab("Day of the Week")
  
```


## Problem 3
Loading the data
```{r}
data("ny_noaa")

ny_noaa =
  ny_noaa %>%
  as_tibble(ny_noaa) %>%
  janitor::clean_names() %>%
  separate(date, c("year", "month", "day"))%>%
  mutate(tmax = as.integer(tmax), tmin = as.integer(tmin))
```
